The Astropy Project:

### 2017-10-03 main.tex
units new features
Update on Overleaf.

\begin{description}\itemsep0ex
    \item[Local Earth coordinate frames] In addition to representing celestial
    coordinates, \astropypkg\ now supports specifying positions on the Earth in
    a number of different geocentric systems with the \texttt{EarthLocation}
    class.
    With this, \astropypkg\ now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \texttt{Time} class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg\ or the
    \astropy-affiliated package \texttt{astroplan} (TODO: cite zenodo entry?).

@@

\subsection{Robust Statistical Estimators}
\subsection{Circular Statistics}
\subsection{Lomb-Scargle Periodograms}
\subsection{Ripley's K Function Estimators}
\subsection{Histogram Binning}

>>>>

\begin{description}
    \item[Local Earth coordinate frames] In addition to representing celestial
    coordinates, \astropypkg\ now supports specifying positions on the Earth in
    a number of different geocentric systems with the \texttt{EarthLocation}
    class.
    With this, \astropypkg\ now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \texttt{Time} class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg\ or the
    \astropy-affiliated package \texttt{astroplan} (TODO: cite zenodo entry?).

@@

\subsection{Robust Statistical Estimators}

Robust statistics provide reliable estimates of basic statistics for complex distributions. The \package{stats} package includes several robust statistical functions that are commonly used in astronomy. This includes methods for rejecting outliers as well as statistical description of the underlying distributions.

\subsubsection{Sigma Clipping}

Sigma clipping provides a fast method to identify outliers in a distribution. For a distribution of points, a center and a standard deviation are calculated. Values which are a set number of sigma times the standard deviation away from the center are rejected. The process can be iterated to further reject outliers.

\subsubsection{Median Absolute Deviation}

The median abosolute deviation (MAD) is a measure of the spread of a distribution and is defined as median(abs(a - median(a))). For a normal distribution, the MAD is related to the standard deviation by a factor of 1.4826, and a convenience function is available to apply the conversion.

\subsubsection{Biweight Estimators}

A set of functions are included in the \package{stats} package that use the biweight formalism. These functions have long been used in astronomy, particularly to calculate the velocity dispersion of galaxy clusters [XXX].

\subsection{Circular Statistics}
\subsection{Lomb-Scargle Periodograms}
\subsection{Ripley's K Function Estimators}
\subsection{Histogram Binning}
